\documentclass[9pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{lmodern}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection.}{1em}{}

\begin{document}

\begin{center}
    \Large\textbf{Book III: The Stone That Looped the World} \\
    \large Chapter 2: The Portal that Ate the Sky\\
\end{center}

\vspace{1in}


\begin{enumerate}
    \item \textbf{The Hook} \\
    In a quiet stretch of the western farmlands, an experimental portal hooks into Inanis. There is no announcement. Just a humming field. A flicker in the light. The sky shudders — then bends. The hook is brief, only seconds. But something passes through.

    \vspace{1em}
    \item \textbf{The Haunting Begins} \\
    Shadows move in wrong directions. Footsteps echo ahead of the walker. Children speak with voices they do not have. A newborn goes silent. A farmer sees his wife blink out of the room mid-sentence. The air thickens. Something is in the walls — but has no form.

    \vspace{1em}
    \item \textbf{The Farmlands Break} \\
    A girl walks into a mirror. A man finds his mouth sewn shut in his own handwriting. A family dies mid-meal, eyes fixed on an empty chair. Screams echo from no source. The sky dims for hours, though the sun still burns. The realm of Inanis pushes through — not in body, but in violation.

    \vspace{1em}
    \item \textbf{The Exorcism} \\
    Priotheer arrives alone. He does not speak. He does not run. He walks the field, pressing breath and pattern into the soil. Walls straighten. Shadows revert. The names of the dead fold inward. Time loses its edge. The incursion is erased — mostly.

    \vspace{1em}
    \item \textbf{The Memory Fades} \\
    Those who lived through it do not recall. But they hesitate. A woman pauses, almost naming a brother. A child wakes crying, unsure why. A census shows names no one knows. The land is not haunted. But it is not whole. Priotheer leaves. The world forgets. But not completely.

    \vspace{1em}
    \item \textbf{The Wall is Needed} \\
    Priotheer does not delay. The incident confirms what he feared: the portals cannot be allowed to continue. The Wall must rise, fully. He begins channeling harder, bleeding magic into geometry. The island will close. The next breach might not be survivable.

\end{enumerate}


\newpage

\section*{Segment 1: The Hook}

It began with tools in the wrong places.

\vspace{0.5em}
A hammer found in the kitchen.\\
A brush left upright in water that hadn’t been drawn.\\
Bread cooling before it had been baked.

\vspace{0.5em}
Marna noticed first. Her goat refused to cross the threshold of the barn. It simply stared, eyes locked not on her, but on a space just above her shoulder. When she turned, there was nothing. When she turned back, the goat was gone.

\vspace{0.5em}
She found it inside the walls two days later. Not dead. Just still. Like it had never moved at all.

\vspace{0.5em}
Down the hill, Hedder woke to his fields turned inside out. The dirt was soft on top, but hard beneath---with a seam down the center that pulsed if he looked at it too long. He didn’t tell anyone. Just re-planted and walked with a limp the rest of the week.

\vspace{0.5em}
By the third night, lights came.

\vspace{0.5em}
Not in the sky---but in the grain.\\
Small flares that hovered, stuttering like breath on a mirror.\\
Children chased them. One didn’t come back.

\vspace{0.5em}
No one panicked. Not yet.\\
But windows began to stay shut at dusk.\\
Chickens roosted at noon.\\
People forgot how long they’d been awake.

\vspace{0.5em}
Then came the voice in the well.

\vspace{0.5em}
Low.\\
Clear.\\
Calling names no one in the village had ever heard.

\vspace{0.5em}
A man leaned in to listen.\\
His wife found him hours later---crouched beside the well, head tilted just enough to show he was listening still.

\vspace{0.5em}
He had torn out his own tongue.\\
The name had been his.

\vspace{0.5em}
Still, no one blamed the portal.

\vspace{0.5em}
It had been set in the fallow plot weeks earlier, part of an outreach effort. Just a test coil. Nothing serious. The real work was done in the east.

\vspace{0.5em}
But that coil---buried in a field no one remembered giving permission for---hummed with something too constant.

\vspace{0.5em}
On the fourth night, the stars over the farmlands vanished.

\vspace{0.5em}
Not clouded.\\
Not moved.\\
Just\ldots{} gone.

\vspace{0.5em}
Children asked if the sky had been erased.\\
Parents said, ``no, just sleep,'' and lit more candles.

\vspace{0.5em}
And beneath the soil, something tugged.

\vspace{0.5em}
The breach hadn’t opened. Not fully.\\
But the hook had landed.\\
The portal coil had anchored, for just a moment, to a sliver of Inanis.

\vspace{0.5em}
And Inanis had looked back.

\newpage

\section*{Segment 2: The Haunting Begins}

The doors no longer stayed shut.

\vspace{0.5em}
Not because of the wind.\\
Not because of warping wood.\\
Just---because they didn’t want to.

\vspace{0.5em}
Bolts slid back by unseen hands.\\
Chairs dragged across floors in rooms left empty.\\
Milk curdled overnight, even in stone-chilled cellars.

\vspace{0.5em}
Then the voices started.\\
Not whispers. Not murmurs.

\vspace{0.5em}
\textbf{Clear. Intentional. Mimicry.}

\vspace{0.5em}
At first, they imitated the living.\\
A mother heard her daughter call for her from the attic---but her daughter was outside, playing in the yard.\\
A baker answered the door to the sound of his own voice saying, ``I forgot something.''\\
The door was open. Nothing was there.

\vspace{0.5em}
Then came the repetitions.

\vspace{0.5em}
One man sat at his table and spoke his own name over and over for hours---voice steady, eyes closed. He stopped when a neighbor shook him. He had no memory of the event, but his tongue was swollen and bleeding from overuse.

\vspace{0.5em}
Another began setting the dinner table for nine---though he lived alone, and only owned six chairs. He kept asking where the others had gone.

\vspace{0.5em}
In the fields, animals went missing.\\
Not all at once. Not messily.

\vspace{0.5em}
Just\ldots{} gone.\\
Troughs still filled.\\
Gates still closed.\\
No blood. No sound.

\vspace{0.5em}
But worst were the reflections.

\vspace{0.5em}
The mirror in the chapel showed a wedding every night---always the same couple.\\
No one recognized them.\\
But one old man wept when he saw them, saying only, ``I knew her.''

\vspace{0.5em}
Another mirror refused to show anything at all, even when held to the sun.

\vspace{0.5em}
A boy disappeared trying to chase his own shadow, laughing the entire way.

\vspace{0.5em}
The sky remained blank.

\vspace{0.5em}
And the portal coil---that buried, humming node in the empty fallow field---now pulsed once every hour. The pulse was felt in the soles of feet and behind the teeth.

\vspace{0.5em}
People began to whisper ``burn it.''\\
But no one did.\\
No one wanted to get close enough.

\vspace{0.5em}
By the sixth night, a low tone hummed across the farmlands---not from the coil, but from the \textbf{soil} itself.\\
It rose only at night.\\
And it said no word.\\
But it \textit{waited}.

\vspace{0.5em}
And in one home, a child climbed onto the ceiling and would not come down.

\newpage

\section*{Segment 3: The Farmlands Break}

On the seventh night, the wind reversed.

\vspace{0.5em}
It didn’t blow.\\
It pulled.\\
Out of windows, out of lungs, out of memory.

\vspace{0.5em}
A woman tried to scream and exhaled a name she had never learned.\\
A horse collapsed mid-stride, its shadow still running.\\
Two houses inverted---not exploded, not collapsed, just\ldots{} folded inward, their contents spilling out as whispers and dust.

\vspace{0.5em}
At sunrise, a child was found in the well.\\
Floating, eyes open, dry.\\
No one remembered a child living there.\\
But when they lifted her out, three families began to cry.

\vspace{0.5em}
None could say why.

\vspace{0.5em}
In the barn near the portal coil, the floor rippled.\\
A man sank ankle-deep before it hardened again.\\
He was stuck.\\
He died standing, overnight---eyes wide, as if watching something just above him.

\vspace{0.5em}
Another family gathered for a meal.\\
The food spoiled between blinks.\\
Maggots whispered in the bread.\\
When they fled the house, it closed behind them and would not reopen.

\vspace{0.5em}
One girl disappeared entirely---in front of others.\\
She reached for her father’s hand and became light, then smoke, then smell, then nothing.

\vspace{0.5em}
The chapel bell rang once.

\vspace{0.5em}
Only once.

\vspace{0.5em}
No one had pulled the rope.

\vspace{0.5em}
At that sound, all the windows on the western side of every home cracked outward.\\
Not shattered---cracked. As if pushed from within.

\vspace{0.5em}
That was when the screams began.

\vspace{0.5em}
Real ones.\\
Not echoed. Not imitated.\\
From people still alive.

\vspace{0.5em}
And not for long.

\vspace{0.5em}
A farmer walked into his mirror and burst like glass across the room.\\
A baby cried itself inside out.\\
The shepherd was found suspended mid-air, arms splayed, humming.

\vspace{0.5em}
No one tried to leave.\\
No one could remember the way.

\vspace{0.5em}
The portal coil had stopped pulsing.\\
Now it was still.\\
As if it had done what it came to do.

\vspace{0.5em}
And at the edge of the farmlands, standing on a broken fence post,\\
a shadow with no source turned to face the Stone Tree.

\vspace{0.5em}
And smiled.

\newpage

\section*{Segment 4: The Exorcism}

Priotheer did not arrive with light.

\vspace{0.5em}
There was no storm, no chorus, no heralds.

\vspace{0.5em}
Only a figure stepping barefoot into the edge of the field just after sunset---while the sky was still refusing to be night.

\vspace{0.5em}
He did not speak.

\vspace{0.5em}
Not to the survivors.\\
Not to the dead.\\
Not to the thing that watched from behind the walls of air.

\vspace{0.5em}
He walked past the coil---now inert, quiet as bone---and pressed his hand to the soil.

\vspace{0.5em}
It trembled.

\vspace{0.5em}
Not from fear.\\
From recognition.

\vspace{0.5em}
He walked clockwise---one slow ring, heel to toe, around the farmlands.

\vspace{0.5em}
Behind him, grass turned dark.\\
Chalk lines appeared and vanished.\\
Shadows stopped moving.

\vspace{0.5em}
When he reached the well, he stopped.

\vspace{0.5em}
Bent.

\vspace{0.5em}
Whispered into it---not words, but \textbf{weight}.

\vspace{0.5em}
The stone lining wept.\\
The rope frayed.\\
The water fell upward for a moment, then stilled.

\vspace{0.5em}
He rose and passed through each broken threshold: house, barn, kitchen, chapel.

\vspace{0.5em}
In every room he whispered.\\
And in every whisper something retreated.

\vspace{0.5em}
The air stopped pressing.\\
Mirrors returned to silence.\\
And the smile on the fence post vanished---not from fear, but from closure.

\vspace{0.5em}
It was not a battle.\\
It was not cleansing.

\vspace{0.5em}
It was \textit{revision}.

\vspace{0.5em}
The wound was not healed.\\
But it was now \textit{unhappened}---just enough.

\vspace{0.5em}
What could not be reversed was \textbf{erased}.\\
What could not be erased was \textbf{blurred}.

\vspace{0.5em}
The names of the dead no longer appeared in records.\\
Their homes rebuilt themselves in wrong configurations.\\
Families wept in the mornings and did not know why.

\vspace{0.5em}
And Priotheer, standing beneath the Tree once again, pressed a pebble into the soil.

\vspace{0.5em}
He did not speak.\\
But if he had, it might have been:

\vspace{0.5em}
\textit{``This cannot happen again.''}


\newpage

\section*{Segment 5: The Memory Fades}

The farmlands were quiet.

\vspace{0.5em}
The coil was gone.\\
No one remembered removing it.\\
The field was fallow, but freshly turned---as if expecting seed that no one planned to plant.

\vspace{0.5em}
A census clerk noted a gap in the western boundary, then shrugged and filed it under ``unmeasured tract.''\\
A surveyor penciled in homes she thought she’d seen but couldn’t find again.

\vspace{0.5em}
A girl walked to school alone and asked her teacher where her brother was.\\
The teacher asked for a name.\\
The girl blinked.\\
Then laughed.

\vspace{0.5em}
\textit{``I don’t have a brother. I don’t think I ever did.''}

\vspace{0.5em}
Her shoes were different sizes that day.

\vspace{0.5em}
Elsewhere, a baker set eight loaves on the counter and found only seven when he turned around.\\
He re-counted three times.\\
Then decided he had imagined the eighth.

\vspace{0.5em}
A family sat to dinner and used one extra chair.\\
No one said why.\\
No one asked.

\vspace{0.5em}
In the chapel, the mirror had been removed.\\
But its reflection lingered---for just a second---in the polished brass of the candelabra.

\vspace{0.5em}
A woman sweeping the steps looked up once and felt her heart stop.\\
She did not remember why.\\
She finished sweeping.

\vspace{0.5em}
The town moved on.

\vspace{0.5em}
It always had.

\vspace{0.5em}
The priest forgot his own sermons, but preached them anyway.\\
The mayor wept during a meeting and claimed it was from the dust.\\
Children skipped songs missing verses no one recalled forgetting.

\vspace{0.5em}
And every few days, someone would pause mid-thought.\\
Mid-step.\\
Mid-sentence.

\vspace{0.5em}
As if something had pulled at them.

\vspace{0.5em}
And then they would continue---smiling, nodding, changing the subject.

\vspace{0.5em}
There were no graves.\\
No records.\\
No warnings.

\vspace{0.5em}
The farmlands became farmland again.\\
Wheat was planted.\\
Hedges trimmed.

\vspace{0.5em}
But no house stood for long.\\
No fence held its line.

\vspace{0.5em}
And deep beneath the soil,\\
in a silence thick enough to settle over names never spoken,\\
the shape of what had happened folded inward and stayed.

\vspace{0.5em}
Not erased.\\
Not remembered.

\vspace{0.5em}
Just gone.

\newpage

\section*{Segment 6: The Wall is Needed}

The next morning, Priotheer stood alone on the northern bluff.

\vspace{0.5em}
The wind bent around him.\\
Not against him. Not through him.\\
Just\ldots{} around.

\vspace{0.5em}
He had not slept.\\
He no longer needed to.

\vspace{0.5em}
In his hand, he held the remnant of a name---not written, not spoken. Just the shape of something that had once been remembered. It pulsed faintly, then faded. He let it go. The breeze did not take it.

\vspace{0.5em}
Behind him, Orfyd breathed in peace.

\vspace{0.5em}
Markets opened.\\
Children laughed.\\
A woman stitched a dress from a pattern she didn’t recall designing.

\vspace{0.5em}
No one knew what had been lost.

\vspace{0.5em}
But Priotheer did.

\vspace{0.5em}
And it was enough.

\vspace{0.5em}
The portal program in the east had been suspended.\\
The coils dismantled.\\
The engineers reassigned.

\vspace{0.5em}
But he knew that wasn’t enough.\\
Knowledge lingered.\\
Curiosity slept lightly.

\vspace{0.5em}
The rift in the farmlands had not just taken lives.\\
It had shown what the world still risked---with every connection, every tether, every breach.

\vspace{0.5em}
So he walked.

\vspace{0.5em}
Not to speak. Not to warn.

\vspace{0.5em}
To finish.

\vspace{0.5em}
The Wall had been rising for months, quietly---a shape beneath the shape of the world.\\
Now it would close.

\vspace{0.5em}
Fully.\\
Deliberately.\\
Permanently.

\vspace{0.5em}
He returned to the Tree and placed a stone---not from the island, but from the border where the last flame had steadied.

\vspace{0.5em}
He whispered the final loop.

\vspace{0.5em}
The glyphs beneath the soil brightened, then dimmed.

\vspace{0.5em}
Birdsong shifted pitch.

\vspace{0.5em}
The stars that night blinked once---in unison---and aligned slightly out of memory.

\vspace{0.5em}
And in the morning, Orfyd was closed.

\vspace{0.5em}
Not in prison.

\vspace{0.5em}
But in protection.

\vspace{0.5em}
Not walled off.

\vspace{0.5em}
But walled in.

\vspace{0.5em}
The world had not ended.

\vspace{0.5em}
But it had been sealed.

\vspace{0.5em}
And Priotheer, seated once again in the shadow of the Tree, allowed himself---just once---to wonder:

\vspace{0.5em}
\textit{``Will it be enough?''}

\vspace{0.5em}
He did not wait for an answer.

\newpage




\end{document}

