\documentclass[9pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{lmodern}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection.}{1em}{}

\begin{document}

\begin{center}
    \Large\textbf{Book III: The Stone that Refused to Heal} \\
    \large Chapter 1: The World that Refused to Heal\\
\end{center}

\vspace{1in}


\begin{enumerate}
    \item \textbf{The Ash of Waiting} \\
    Orfyd survives the Spiral’s withdrawal, but does not recover. The Priimydians refuse grief. Instead, they turn to action — assembling a secret project to rebuild what was lost. A portal is planned, not to conquer, but to reunite. Beneath the Stone Tree, Priotheer begins to move.

    \vspace{1em}
    \item \textbf{The Portal Begins to Sing} \\
    The prototype hums. Engineers cheer — until it won’t stop. A child vanishes. Sketches grow wrong. The sky blinks. Birds shatter mid-flight. Priotheer walks the marshes in silence, whispering to the soil. Something has been disturbed.

    \vspace{1em}
    \item \textbf{The First Loop} \\
    Priotheer begins raising the Wall. Quietly. Without proclamation. Each step channels old magic, not to seal the realm with force, but to contain it with form. A sailor returns from a straight path. Maps ripple. Pebbles do not stay where they are placed. The world is beginning to curl.

    \vspace{1em}
    \item \textbf{What Came Through} \\
    The portal opens once more — not for travel, but breach. A shape steps in: not beast, not god, just wrong. A house dissolves. A dog returns from death. A scream echoes with no throat. Priotheer does not confront it. He corrects it — and adds another line to the loop.

    \vspace{1em}
    \item \textbf{The Shape That Seals} \\
    The final fracture confirms it. Priotheer walks the island, pressing memory into earth, blood into stone. Ships turn back without turning. Language loses tension. Mirrors forget. He does not pause. He knows the next breach may not be reversible.

    \vspace{1em}
    \item \textbf{The Circle That Forgot Its Center} \\
    No one notices. The Wall’s rise is seamless. The seasons blur. Time moves faster, but none are aware. The people call it peace. Priotheer is no longer seen. The Tree remains untouched. “Beyond” is a word that slowly fades from common speech.

    \vspace{1em}
    \item \textbf{The Loop Sealed} \\
    At dawn, Priotheer completes the Wall. There is no ceremony — only silence. He sits beside the Tree. Not asleep, not dead. Just present. His name begins to fade from memory. The world continues, bounded, unknowing. The Spiral is gone. The Pattern is quiet. But the loop — held.
\end{enumerate}


\newpage

\section*{Segment 1: The Ash of Waiting}

The Spiral was gone.

\vspace{0.5em}
No rites followed it. No songs marked its end. The people of Orfyd simply woke one day and no longer felt it---like losing a voice they never knew they had until it went silent.

\vspace{0.5em}
They did not speak of it. Not because they had moved on, but because they hadn't.

\vspace{0.5em}
The priests folded their robes and took to calendars. The dream-keepers left their posts and became architects. A handful of scribes, formerly trained in resonance-calligraphy, now recorded rainfall, tidal motion, and grain output.

\vspace{0.5em}
They did not call it grief.\\
They called it strategy.

\vspace{0.5em}
Because what they did speak of---often, fiercely, always with eyes slightly too wide---were the others.

\vspace{0.5em}
The ones still out there.

\vspace{0.5em}
Their brothers in Aerul. Their daughters in Isfyd. The cousins lost in the marsh of Palus. The ones trapped behind the fracture when the fifth flame held and the world came apart.

\vspace{0.5em}
They had not died.\\
That much was clear.\\
No messenger had confirmed otherwise.

\vspace{0.5em}
And so the Priimydians of Orfyd, unwilling to bury what could still be saved, turned their gaze to the horizon.

\vspace{0.5em}
If the world could tear, it could also be stitched.

\vspace{0.5em}
This was not said aloud by Priotheer. He said less and less now. But in the council chambers and the libraries and the shallow halls where discourse still clung like moss, one idea bloomed like rot beneath polished stone:

\vspace{0.5em}
\textit{``We must build a way back.''}

\vspace{0.5em}
The portal project began without name, without banner.\\
It grew from sketches, passed hand to hand.\\
From words etched on napkins, from diagrams carved in damp walls.\\
A theory first, then a scaffold. Then a hum beneath the floor.

\vspace{0.5em}
None of them questioned the source of the power.\\
None of them asked why the portal glowed in ways their new science couldn’t explain.\\
They only asked when it would be ready.

\vspace{0.5em}
Not ready to explore.\\
Not ready to conquer.

\vspace{0.5em}
Ready to reunite.

\vspace{0.5em}
Because they had not let go.\\
Because they had seen too much, but knew too little about what could be lost.\\
Because if they could open one door, maybe the world could untear.

\vspace{0.5em}
And in the shade of the Stone Tree, Priotheer sat alone.

\vspace{0.5em}
He felt the weight of time gathering in his limbs.\\
He felt the earth begin to curl inward---not in pain, but in response.\\
And he said nothing.

\vspace{0.5em}
Because they still had hope.\\
And he, more than any man alive, knew what hope could cost.


\newpage


\section*{Segment 2: The Portal Begins to Sing}

It was never supposed to make a sound.

\vspace{0.5em}
The first portal prototype was little more than a circle of bent steel wrapped in copper coils, arrayed on a floating platform. Its designers claimed it would hum only when calibrated---and then remain silent until activated.

\vspace{0.5em}
But on the third night of calibration, it began to sing.

\vspace{0.5em}
No melody. No words. Just a low, impossible tone that vibrated under the skin and made water ripple in still basins.

\vspace{0.5em}
At first, they celebrated.

\vspace{0.5em}
``It responds!'' one engineer shouted. ``It’s harmonizing with something!''\\
One priest muttered a half-forgotten chant under his breath---a ritual of alignment meant for sacred bells, not machines. It didn’t help.

\vspace{0.5em}
The sound didn’t stop.

\vspace{0.5em}
It wasn’t loud, just ever-present. Like a breath that wasn’t yours, drawn too close.

\vspace{0.5em}
Then came the anomaly in the sky.

\vspace{0.5em}
On the fifth night, a star in the southern belt blinked---not faded, not fell---just blinked, twice, as if a hand had passed before it. Observers noted it. Then dismissed it.

\vspace{0.5em}
But the lead architect did not sleep.

\vspace{0.5em}
She stood before the portal, sleepless, sketching in charcoal---not the machine, but what she saw on the other side. No one else saw anything. But her sketches grew stranger.

\vspace{0.5em}
Not figures. Not beasts.

\vspace{0.5em}
Just wrongness.

\vspace{0.5em}
Angles with teeth.\\
Grids that pulsed.\\
A ladder with no bottom.

\vspace{0.5em}
She tore up the first dozen, then stopped tearing. She didn’t know why.

\vspace{0.5em}
By the seventh night, a boy fell into the platform basin and was pulled under---not by current, but by still water.

\vspace{0.5em}
He did not resurface.

\vspace{0.5em}
The search party recovered only his boots, and one word etched into the stone rim of the portal in wet, charred lettering:

\vspace{0.5em}
\textit{``Home.''}

\vspace{0.5em}
No one could explain it.

\vspace{0.5em}
The priest said it was a trick of runoff and guilt.

\vspace{0.5em}
The engineers sealed the platform---temporarily, they said.

\vspace{0.5em}
But in the week that followed, two birds flew into each other mid-air and shattered.\\
A cow gave birth to a calf with two hearts and no eyes.\\
And the river that fed the marsh reversed for one hour, then righted itself---as if embarrassed.

\vspace{0.5em}
Priotheer, when told, said only:

\vspace{0.5em}
\textit{``It’s beginning too soon.''}

\vspace{0.5em}
He was seen, later that night, walking barefoot around the Tree.

\vspace{0.5em}
One step at a time.\\
One breath with each motion.\\
Drawing lines no one else could see.

\newpage

\section*{Segment 3: The First Loop}

It began with a pebble.

\vspace{0.5em}
Priotheer knelt at the eastern bluff before sunrise, picked up a pebble no larger than a fingernail, and placed it beside a carved groove in the earth. He whispered something---not a spell, not a prayer---and moved on.

\vspace{0.5em}
At noon, he returned to the same bluff and found the pebble exactly where he’d left it.\\
He moved it one hand-width west and whispered again.

\vspace{0.5em}
That night, he returned.

\vspace{0.5em}
The pebble had returned to its first position.

\vspace{0.5em}
He said nothing.\\
Only nodded.

\vspace{0.5em}
It had begun.

\vspace{0.5em}
The Wall would not rise like a monument.\\
It would not crack sky or tear sea.\\
It would loop---quietly, iteratively, invisibly at first---like a thought repeating itself until it forgot it was ever new.

\vspace{0.5em}
Priotheer’s magic was not one of force, but of form.\\
He did not summon.\\
He aligned.

\vspace{0.5em}
Each hour spent channeling near the Tree drew on some deeper reserve within him---not just memory, but something older, seeded in him when the Spiral first curved toward the Pattern.

\vspace{0.5em}
This was his purpose. Not to rule. Not to lead.

\vspace{0.5em}
But to seal.

\vspace{0.5em}
He never said the word ``Wall.''\\
He never told the council.\\
He simply walked---drawing lines with heel and finger, pressing his breath into soil and salt and glass.

\vspace{0.5em}
He knew the consequences.

\vspace{0.5em}
When the Wall completed its loop, it would render the island whole.\\
Unreachable.\\
Unleavable.\\
Safe.

\vspace{0.5em}
And cursed.

\vspace{0.5em}
Because no spell was without shape, and no shape without a cost.

\vspace{0.5em}
Already the edges of things had begun to blur. A sailor charted a new coast only to find it mirrored his own. A scholar returned to a ruined temple that had not existed the week before. A child drew a map in sand that showed five rivers where there had only been two.

\vspace{0.5em}
Priotheer marked these changes---not with worry, but with rhythm.

\vspace{0.5em}
It was working.

\vspace{0.5em}
He would finish it slowly, quietly.\\
He would give the people no reason to fear.\\
And when it was done, they would be safe---from the portals, from the rifts, from the war none of them yet knew was coming.

\vspace{0.5em}
He placed another pebble.\\
Moved one step west.

\vspace{0.5em}
The Wall turned---not upward, but inward.\\

But not all on Orfyd remained within its bounds.\\

A handful of ships had already sailed — long before the Wall took shape.\\

Explorers, outcasts, the doubting and the restless.\\

They slipped into the open waters without knowing they were escaping anything at all.
In time, their descendants would be called Illurians, Cenedians, Monunarians, and names not yet dreamed.\\

They would build cities from memory they barely retained.\\

They would make stories out of echoes.
And they would call the place they left behind myth — or mistake.\\

But, for now, they were saved from what was soon to come.

\newpage

\section*{Segment 4: What Came Through}

They called it a calibration window.

\vspace{0.5em}
Just a moment of full channeling. Enough to confirm targeting, they said. Enough to trace a signature across realms.

\vspace{0.5em}
They did not call it what it was: \textit{an opening}.

\vspace{0.5em}
The platform was reactivated three days after the boy disappeared. The incident was ruled a misstep, a flaw in structure. The architects were rotated out. The magical power structures were redrawn. The copper rings re-forged.

\vspace{0.5em}
And on the eighth day, the portal blinked open.

\vspace{0.5em}
It didn’t roar.\\
Didn’t flare.

\vspace{0.5em}
It simply shimmered, like light moving through water that had forgotten it was wet.

\vspace{0.5em}
The watching crowd held their breath.

\vspace{0.5em}
And then, something stepped through.

\vspace{0.5em}
Not a creature.\\
Not a soldier.\\
Not a message.

\vspace{0.5em}
A shape.

\vspace{0.5em}
Thin.\\
Curved.\\
Folded.

\vspace{0.5em}
Like a shadow cast by nothing, bent the wrong way.

\vspace{0.5em}
It made no sound.\\
It left no footprints.

\vspace{0.5em}
It stood still at the edge of the platform for seven seconds. Then turned---not its body, but the world around it---and vanished.

\vspace{0.5em}
One child fainted.\\
Two priests vomited.\\
An old woman wrote a song in a language she had never heard.

\vspace{0.5em}
The engineers sealed the site again.

\vspace{0.5em}
But the next night, a farmhouse in the hills dissolved.

\vspace{0.5em}
No heat.\\
No rubble.

\vspace{0.5em}
Just a clean absence. As if the house had been a suggestion the world had decided not to follow anymore.

\vspace{0.5em}
A dog was found in its place---identical to one that had died a year before.

\vspace{0.5em}
Its eyes did not blink.\\
It did not breathe.\\
But it followed commands.

\vspace{0.5em}
By morning, it was gone.

\vspace{0.5em}
And Priotheer, standing beneath the Tree with his hand pressed into the earth, whispered the shape of a spiral not as a memory, but as a ward.

\vspace{0.5em}
Then he placed another pebble.

\newpage

\section*{Segment 5: The Shape That Seals}

The day after the portal incident, the sky above the southern coast.

\vspace{0.5em}
Not visibly.\\
Not with lightning or rupture.\\
Just---differently.

\vspace{0.5em}
Birds avoided it.\\
Clouds parted for no reason.\\
And three different cartographers, working independently, drew it on their charts without realizing what it was.

\vspace{0.5em}
It lasted twelve hours.\\
Then was gone.\\
Or had never been.

\vspace{0.5em}
Priotheer did not visit the portal site again.

\vspace{0.5em}
He walked the coast.\\
He stepped barefoot through the shale and tidefoam.\\
He whispered shapes into sand, letting them vanish with the next wave.

\vspace{0.5em}
When he reached the western cape, he placed a hand on the stone bluff and said the words he had been avoiding since the last flame held:

\vspace{0.5em}
\textit{``It is enough.''}

\vspace{0.5em}
That night, he did not sleep.

\vspace{0.5em}
He sat beneath the Tree.\\
He pressed both hands to the roots.\\
And he let the Wall begin to rise.

\vspace{0.5em}
Not all at once.\\
Not visibly.

\vspace{0.5em}
But something shifted in the way the wind bent around the island.

\vspace{0.5em}
Boats attempting to leave began to return---confused, circled, convinced they had lost their heading.\\
Messages sent across the ocean returned unopened, marked unreadable.\\
Mirrors began to double, then forget, then reflect only faces already gone.

\vspace{0.5em}
The people whispered of coincidence.\\
The scholars whispered of harmonics.\\
No one whispered of Priotheer.

\vspace{0.5em}
Because no one knew.

\vspace{0.5em}
Except the Tree.\\
And maybe the sea.

\vspace{0.5em}
And on the third day of channeling, Priotheer coughed blood into his palm.

\vspace{0.5em}
He wiped it against his robe and kept working.

\vspace{0.5em}
Because there was no longer time.\\
Because something had stepped through.\\
Because if he did not finish, the world would come apart again.

\vspace{0.5em}
He drew a final line in the dirt beside the Tree.

\vspace{0.5em}
The ground held the shape.

\vspace{0.5em}
He nodded once, and whispered:

\vspace{0.5em}
\textit{``Loop.''}

\vspace{0.5em}
And somewhere, far away, a boundary closed.

\newpage

\section*{Segment 6: The Circle That Forgot Its Center}

No one noticed when the Wall closed the island on which Priimydia stood off from the rest of the world.

\vspace{0.5em}
No bells tolled.\\
No sea changed color.\\
No traveler reported vanishing cliffs or melting paths.

\vspace{0.5em}
Because nothing seemed to change at all.

\vspace{0.5em}
Ships still sailed.\\
Fields still ripened.\\
Children played in spirals they didn’t know they were repeating.

\vspace{0.5em}
Only one thing shifted---and it could not be measured:

\vspace{0.5em}
\textbf{Rhythm.}

\vspace{0.5em}
Days began to blur.\\
Seasons shortened without alarm.\\
A harvest festival was held early---not because anyone planned it that way, but because it felt right.

\vspace{0.5em}
No one noticed that time had begun to run faster.\\
No one remembered what it had felt like before.

\vspace{0.5em}
Clerks recorded appointments they didn’t remember scheduling.\\
Stonemasons laid foundations for projects no one recalled approving.\\
A teacher began a lesson again---and no student questioned it.

\vspace{0.5em}
These were not anomalies.

\vspace{0.5em}
They were\ldots{} ordinary.

\vspace{0.5em}
Magic had faded long before.\\
The Spiral had gone quiet.\\
This was simply the world, turning as it always had.

\vspace{0.5em}
Only now, it turned inward.

\vspace{0.5em}
No one left.\\
Not truly.

\vspace{0.5em}
Boats still pushed out from the docks, but they always returned---sometimes from the wrong direction, sometimes with more fish than made sense.

\vspace{0.5em}
Maps no longer held tension.\\
Cartographers no longer argued.\\
The shape of the island simply was---whatever shape it chose that season.

\vspace{0.5em}
Priotheer was not seen again.

\vspace{0.5em}
The Tree remained untouched.

\vspace{0.5em}
Its roots still pulsed, though no one felt them.\\
Its bark still shimmered, though no one looked directly.\\
Its leaves fell at odd times, but no one swept them.

\vspace{0.5em}
The people of Priimydia called this peace.

\vspace{0.5em}
No more flames.\\
No more gods.\\
No more strange incursions.

\vspace{0.5em}
The portal was never spoken of again.

\vspace{0.5em}
No monuments were raised.\\
No laws were passed.\\
Only one word slowly vanished from common speech:

\vspace{0.5em}
\textit{Beyond.}

\vspace{0.5em}
And the world, as they knew it, held.

\vspace{0.5em}
Not with truth.\\
Not with memory.

\vspace{0.5em}
But with silence.

\newpage

\section*{Segment 7: The Loop Sealed}

He finished at dawn.

\vspace{0.5em}
There was no final stone, no blaze of light, no sigil drawn in blood or gold.

\vspace{0.5em}
Just one more breath beneath the Tree.

\vspace{0.5em}
One final step around the roots.

\vspace{0.5em}
And the Wall was done.

\vspace{0.5em}
No one felt it close.\\
No one marked the hour.

\vspace{0.5em}
But far beneath the soil, in lines even the roots could not trace, something circled inward and locked.

\vspace{0.5em}
The island was whole.

\vspace{0.5em}
Contained.

\vspace{0.5em}
And unknowing.

\vspace{0.5em}
Priotheer sat down beside the Tree. Not against it---beside it. As if to keep it company.

\vspace{0.5em}
His hands no longer glowed.\\
His voice no longer whispered.\\
The air around him was still.

\vspace{0.5em}
He did not sleep.\\
He did not die.

\vspace{0.5em}
He simply remained.

\vspace{0.5em}
A man hollowed by purpose.\\
Fulfilled by silence.\\
Bound by the shape he had made.

\vspace{0.5em}
Birds flew overhead. They did not see him.\\
Children passed through the clearing. They did not notice him.\\
Even the wind forgot to stir his robe.

\vspace{0.5em}
He was not invisible.\\
Just unasked-for.

\vspace{0.5em}
The magic that had once lived in his blood had become geography.\\
And geography does not speak.

\vspace{0.5em}
The Stone Tree shimmered once, then stilled.

\vspace{0.5em}
And time continued---faster now, but softer.\\
The people of Priimydia woke, worked, aged.\\
They dreamed less.\\
They questioned less.

\vspace{0.5em}
They grew clever.\\
They grew structured.\\
They grew apart from the pattern that once whispered beneath their feet.

\vspace{0.5em}
And they did not know it had ever whispered at all.

\vspace{0.5em}
Only the Tree remembered.

\vspace{0.5em}
Only the Wall held.

\vspace{0.5em}
And Priotheer, whose name would fade into falsehoods and fragments, remained seated---watching a world he had sealed forget why it had needed sealing in the first place.

\vspace{0.5em}
Not in mourning.\\
Not in pride.

\vspace{0.5em}
But in peace.

\vspace{0.5em}
And when the last leaf of the season fell beside him, he closed his eyes.

\vspace{0.5em}
The spiral did not turn.\\
The Pattern did not respond.

\vspace{0.5em}
But the loop---\\
held.


\end{document}

