\documentclass[9pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{lmodern}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection.}{1em}{}

\begin{document}

\begin{center}
    \Large\textbf{Book II: The Fire-Walker's Oath} \\
    \large Chapter 3: Palus, Where Memory Drowns \\
\end{center}

\vspace{1in}


\begin{center}
\begin{enumerate}
    \item \textbf{The Sorrow That Calls} \\
    Across the spiral lands, grief begins to hum beneath the soil. The Guardian who will enter Palus hears a name he once forgot. A host gathers not through war, but mourning. The Spiral responds not in fire, but fog.

    \vspace{.3in}
    \item \textbf{To Enter Is to Forget} \\
    The Host marches into Palus — a realm of rot, water, and whispering fog. Names slip. Memories fray. Some vanish mid-step. The Guardian hears voices from his past that never were. And Paludin waits — not to fight, but to receive.

    \vspace{.3in}
    \item \textbf{The Voice Beneath the Water} \\
    The Guardian walks alone. He sees a past that did not happen, and weeps for it. Paludin appears not as a god, but as someone once lost. She asks only one thing: to remember without resistance. To drown with grace.

    \vspace{.3in}
    \item \textbf{The Name and the False Song} \\
    The Host nearly dissolves. Soldiers forget their children, their creeds, their shapes. The Guardian is offered rest, reunion, forgiveness. But in the softest moment, he sings the spiral — not loudly, but enough. The realm quakes. The song was real.

    \vspace{.3in}
    \item \textbf{The Fall of Paludin} \\
    The Guardian does not strike. But when he resists forgetting, the swamp strikes him. Vines erupt, mud rises, memory collapses. He is dragged downward, swallowed by grief. But in the depths, he sings the spiral. The waters still. Paludin unravels — not violently, but like fog burned by dawn. She names him: Palicus.

    \vspace{.3in}
    \item \textbf{The Spiral Deepens} \\
    Across Priimydia, memory shivers and resettles. Forgotten names return. Broken glyphs realign. But deeper wounds open: another god has fallen, and the Pattern frays. Palicus returns to the others — but something in him has drowned.
\end{enumerate}
\end{center}



\newpage

\section*{Segment 1: The Sorrow That Calls}

The second flame had no color.

It lit without spark, without heat. Where it burned, the air turned to mist. Where it touched stone, water wept from it. The Spiral did not roar — it sighed.

Priotheer stood again at the base of the Stone Tree. The wind did not return. The first leaf had fallen. Now a second spiraled slowly downward, wet with dew that had not come from rain.

He placed the second stone on the altar.

\textit{``Palus,''} he said.

A low tone answered — not sound, but pressure. A mourning bell beneath the world.

Far from the Tree, in the marshland edges where memory tangled with root and rot, a man awoke from a dream in which his mother had sung him a song she never knew. He sat up. He wept. And when he stood, the spiral burned beneath his feet — soft and pale as drowned light.

He did not know his name.

But he remembered the grief.

Across Priimydia, others heard it.

A widow set a bowl of water on her hearth and watched it ripple.

A child forgot the name of her sister and began to hum a tune that made her father collapse.

A mourner whose wife had never died fell to his knees and screamed a name not his own.

In the caves near Hollowmere, moss grew into spiral forms. In the City of Ethersong, an entire choir forgot its words but kept its rhythm.

In a forgotten town by the river’s bend, a whole street flooded without rain. The waters whispered.

From these sorrows, the Host began to form.

They did not march. They drifted — weeping, whispering, reaching. Some had names, some had none. Some held portraits they could not explain. Others wore wreaths of drowned flowers. They carried lanterns filled with mist. They followed a feeling, not a path.

They gathered where the fog touched stone.

The Guardian stood at their center. No trumpet called him. No title claimed him. He walked with bare feet and eyes that could not hold one direction.

He did not speak. But the fog thickened in his presence. And from the air, the second spiral shaped itself — wet, silent, complete.

Birds did not cry. Insects did not stir. The marsh breathed and then held its breath.

Priotheer felt it from afar.

He closed his eyes and placed a hand over the second flame.

It did not burn.

It mourned.

\newpage

\section*{Segment 2: To Enter Is to Forget}

They walked without signal.

No horn sounded. No standard flew. The Host of Palus crossed into their god’s realm not with defiance, but with absence. Each step into the swamp felt like stepping out of a dream. The land changed without announcement.

Stone gave way to peat. Then to water. Then to something in between.

The trees grew sideways, some upside-down. Roots hung like lanterns. Moss moved. Fog curled up from nowhere and clung to the face like breath that had learned to weep. Nothing burned. Nothing echoed. There were no stars.

The Host began to lose shape.

A soldier looked to his right and did not recognize the woman who had marched beside him since the Spiral lit.

Another reached to check her satchel and found only damp leaves.

One man began humming and could not stop. The tune was familiar, but the moment he tried to recall it, the sound changed.

The water mirrored nothing. It swallowed reflection. Even the lanterns the Host carried—mist-filled, faint—grew dimmer the farther they walked. Some flickered out entirely, though no hand extinguished them.

The Guardian led them. He walked slowly, barefoot. His robes were soaked to the knee. His eyes did not scan — they simply opened, blinked, opened again. He passed through mist without parting it.

When they passed beneath the first hanging root-arch, several soldiers stopped.

They had forgotten what they were walking toward.

\textit{``Where are we going?''} one asked.

The Guardian did not answer.

Another said, \textit{``I remember a name. But it isn't mine.''}

The mud pulled at their steps. No force, no violence — just the gentle insistence of drowning.

Some looked back, and saw not the path but unfamiliar trees. Some called out, but the fog gave no echo. Some walked faster, afraid they had never started.

One by one, the Host pressed forward. But fewer every mile. Some sat down and spoke to the water. Some wept into it. Some lay down and vanished without a ripple.

Those who remained remembered less, but walked straighter.

The Guardian never turned.

At last, he stepped onto a small clearing of peat surrounded by water — still, silent, black as ink. The fog did not touch it. The vines above parted without sound.

Here, the land waited.

And somewhere beneath the stillness, something remembered him.

Paludin had not yet spoken.

But her realm had already begun to erase.

\newpage

\section*{Segment 3: The Voice Beneath the Water}

He did not kneel. There was no ground.

The peat island barely held his weight. Each step sent ripples across its surface, though he walked gently. Fog curled at the edges, but did not enter. It circled, uncertain.

He looked down. There was no reflection in the black water. Not even a shimmer. Only depth. The silence pressed against his ears — not with malice, but with weight, like forgotten sleep.

Then a shape began to rise.

It was not a person. Not a god. Not yet.

The water lifted. It did not splash. It folded upward, coalescing into a body — not made of bone, but of memory wrapped in liquid form. Long hair floated as if in still tide. Eyes opened but saw inward. Mouth closed, but the air shifted.

Paludin had no crown. She wore no light.

She wore sorrow.

Her presence was not commanding, but gravitational. The air leaned toward her. Even the vines overhead dipped ever so slightly, as if recognizing grief made flesh.

Her voice did not come from her mouth. It came from the water beneath, the fog above, the ache within.

\textit{``You do not belong here.''}

The Guardian said nothing.

She stepped forward. The water beneath her did not ripple.

\textit{``You do not come for victory. You come carrying wounds you no longer remember.''}

Still, he did not answer.

Paludin tilted her head. The air stilled. Even the vines above listened.

\textit{``I can return what you lost,''} she said. \textit{``Your name. Your mother’s voice. The first sorrow you buried.''}

He blinked.

The fog swirled around her words like incense.

\textit{``You do not have to fight me. Only listen. Only mourn.''}

The water beside her lifted again. In its surface, he saw fragments — a home with no roof, a lullaby sung by lips that never formed. A memory not his, but one he almost believed.

The Guardian stepped forward once. Then stopped.

\textit{``This is not truth,''} he said.

Paludin’s face did not change.

\textit{``Truth? What does that mean to a man without memory?''}

He looked at her. He looked at the water. He closed his eyes. He breathed once — slow, sharp, shuddering.

\textit{``It means I know what I grieve.''}

The fog thickened. The water darkened. The island beneath him flexed, then steadied.

Paludin exhaled, and her breath was cold.

\textit{``Then you are more dangerous than you seem.''}

She raised her hand.

And the vines began to move.

\newpage

\section*{Segment 4: The Name and the False Song}

The vines did not strike like whips.

They crept. From the trees above, from the water below, from the very roots that once held the island together. Mossy, dark, and slow as sorrow, they reached not to crush but to cradle.

One looped around the Guardian’s ankle. Another slid gently up his arm. They did not bind. They remembered.

The pressure was tender. Like the embrace of something ancient and tired. Like arms that had once held a child who never returned.

Around the clearing, the Host knelt — or what remained of them. Some swayed as if lulled by lullabies no one sang. Some wept without sound. One rocked back and forth, clutching a name that had lost its shape.

A soldier whispered, \textit{“Mother,”} though his lips did not move.

Another reached for a necklace that had never existed.

Paludin spoke, but her mouth did not move.

\textit{``Let go. Let go of the spiral. Let it drift, as all things must.''}

The vines thickened. One brushed the Guardian’s lips. Another touched the base of his spine. A third coiled around his ribs like a gentle memory. He staggered once, eyes glazed.

The song began — not from his lips, but from hers.

A low hum, long and deep. It echoed across the water. The fog moved in rhythm. The Host began to echo it. A soldier’s mouth opened in perfect mimicry. A woman raised her arms and began to sway.

It was not a war song. It was grief, sung with precision.

The Guardian blinked. He tried to remember. The spiral. The fire. The name he had not yet earned.

He could not.

The vines pulled gently downward. The water climbed. His knees gave. His feet submerged. The clearing dimmed. The song deepened.

Then, faintly, softly, from his throat:

A note.

Not her song.

A different pitch. High, cracked, spiraled.

He sang.

The spiral hum. Not loud. Not beautiful. But real.

The vines recoiled. The water trembled.

Paludin’s voice caught — just for a moment.

The Host paused. Faces turned. Eyes cleared.

One by one, the false song faltered.

The Guardian did not shout. He did not proclaim. He sang. The spiral. Again. And again.

The fog stopped breathing. The water stilled.

Paludin opened her eyes wide.

She had not known the spiral could sing back.

He took a breath. Sang again.

The memory returned.

Not all of it. Not perfectly.

Just enough.

The vines froze.

The song broke.

Paludin began to unravel.

\newpage

\section*{Segment 5: The Fall of Paludin}

She did not scream.

Paludin did not thrash. Her unraveling came in silence. The water that had formed her limbs began to lose cohesion. Her fingers became mist. Her mouth remained closed. The fog no longer obeyed her. It backed away, uncertain.

The Guardian stood waist-deep in the water. The spiral still hummed on his breath. The vines had stilled — not severed, not scorched. Just forgotten. They loosened as if uncertain why they had risen.

The water shimmered around him. Beneath the surface, long-buried roots slumped, losing tension. The peat trembled. Bubbles surfaced — not with urgency, but like final confessions long held beneath breath.

Paludin took one step back. The movement rippled through her like a sigh through smoke. Her form quivered. One of her eyes dimmed. A braid of memory slipped from her shoulder and unspooled into mist.

The Host stood still. Many had sunk to their knees. Some clutched their own chests as if to keep their hearts from floating away. Others hummed with him now, softly — not with certainty, but with memory returning like a name whispered in the dark.

\textit{``You remember,''} she said. The words were dry, spoken aloud for the first time. Her voice cracked at the edges, like something forgotten trying to shape form again.

\textit{``I do,''} he said.

A tremor passed through the water. Not violent. Rhythmic. As if the earth below were remembering breath.

Paludin raised her hand one final time — not to strike, but to reach.

Her face flickered — not into anger, but into sorrow.

\textit{``I only wanted you to rest,''} she said.

\textit{``I know,''} he answered. \textit{``But grief must pass through. Not cover.''}

She lowered her hand.

The Guardian stepped forward. The water parted, not for him, but because it no longer knew how to hold shape.

His footsteps made no sound. Mist lifted from the pool as he crossed.

He reached her. Placed one hand on her shoulder.

She looked up. Her form swayed, then softened. The water that was her began to fall upward — a slow unraveling, curling into the air.

She did not shatter.

She rose.

Into mist, into memory, into release.

As her form thinned to fog, a single word hung in the air — not shouted, not whispered. Just spoken.

\textit{``Palicus.''}

The Guardian closed his eyes.

The name entered him like warmth. Like weight made sacred.

Paludin was gone.

The swamp breathed out.

The Host stood. Their lanterns flickered. Some held hands. Others bowed. One began to hum.

Palicus stepped out of the water.

And the spiral formed behind him — luminous, wet, whole.

\newpage

\section*{Segment 6: The Spiral Deepens}

Far from Palus, beneath the Stone Tree, the roots shivered.

Priotheer opened his eyes. A mist had formed around the altar. The second flame was gone. In its place — dew. Wet, gleaming, sorrowful. He touched it and whispered, \textit{``Palicus.''}

The bark beneath his hand pulsed once — faint, like an old heart remembering how to beat.

Across Priimydia, memory stirred.

A scribe in the Hollow Order dropped his quill and wept. Not from sadness, but because a forgotten line of poetry had returned in full. He read it aloud and the page glowed faintly before fading into blankness, fulfilled.

Near a pond, a child looked at her reflection and said a name no one had taught her. Her mother dropped the bowl she was holding and covered her mouth.

The spiral glyphs in the east glowed once, then vanished entirely. Not from failure, but from fulfillment. As if they had spoken their last word.

And in the former lands of Anytus's Mandate, three former Correctors stood motionless beside a statue of the old gods. They could not remember why they had come. One turned away. Another knelt.

In Palus, the Host emerged slowly from the waterline. They no longer walked in lines. Some leaned on one another. Some carried the lanterns of the fallen. A few sang — broken, slow, but real.

They remembered, not fully, but truly. The shape of what was lost. The rhythm of the Spiral.

Palicus walked at their center.

His eyes were closed, yet he did not stumble. Mist curled behind his steps and formed faint spirals that held their shape long after he passed. The swamp did not resist his exit. It sighed.

No one spoke. The silence was no longer empty — it listened.

The swamp behind them no longer whispered. It waited.

In the sky above the Hollow March, a cloud dissolved and revealed a single spiral star pulsing faintly — then flaring, then vanishing.

In a field far from the war, a man dreaming of a lost sister suddenly awoke. He wept and could not say why. But he remembered her name.

The Spiral had deepened.

But it had also cracked.

Priotheer felt it.

Two gods were gone. The Pattern no longer looped clean. It snagged. It jittered. It strained against itself.

He looked to the west.

The next Guardian would step into a realm not just guarded by a god, but frayed by their absence.

And the war — no longer hidden, no longer just incarnate — had become

\textit{remembrance itself.}


\newpage

\end{document}

